Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
finished ux writeup

\subsection{Results}
\indent \indent This experiment uncovered a powerful vector for attack, an unlikely source
of usability issues, and insight into how to better communicate to users so that they can be 
empowered to use Tor Browser and its advanced settings. 
Because of the limited size of the study, it's not possible to state with confidence what 
fraction of users will encounter major usability obstacles. However, it was effective at discovering 
and demonstrating issues that are likely to cause problems for many users. 
People did have difficulty with installing Tor Browser (principally because of the Gatekeeper 
code-signing feature on OS X), did not understand what many of the toolbar options meant, 
and were confused by most Tor-specific behaviors. For specific problems 
encountered by an individual user, we refer you to our resources online.

@@

There was one participant who did not pick the first search result, but to save themselves
time while completing the task: 
\begin{quote}{\it
``\ldots so I am going to type in `tor mac download'.
And that gives me some suggestions. I pick the first one.''} \mbox{---P4}
\end{quote}

@@

\subsubsection{Fighting Mac's Security Features}
The biggest usability struggle was the result of tensions between Mac's security feature 
and Tor's usability, rather than a specific feature of the Tor Browser itself.

@@

\subsubsection{On Visual Communication}
Through observing our participants, 
we believe visual elements into their user interface design may be the key to 
communicating with users.

@@

\begin{quote}{\it
``Don't open documents downloaded through Tor\ldots\ That doesn't make sense to me.
But I'll just pay attention because it's in capitals and it's like they're yelling at me.''} \mbox{---P1}
\end{quote}

\subsubsection{User Comprehension} 
Most of our participants did not have the expertise to understand 
the advanced setting for Tor Browser, and were wary to user it, but explaining why an option 
tis available to the user may increase comprehension and tailored use.

@@

@@

@@

@@

\noindent If you would like to observe individual participants' cognitive walkthroughs, 
we transcribed the audio files from our experiment
and synced them to the screen capture we took during the duration of the experiment.
Figure~\ref{walkthrough} shows a screenshot of one of the videos.
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
\end{itemize}

>>>>

\subsection{Results}
\indent \indent This experiment uncovered a powerful vector for attack, an unlikely source
of usability issues, and insight into how to better communicate to users so that they can be 
empowered to use Tor Browser and its advanced settings.

@@

There was one participant who did not pick the first search result, but to save themselves
time while completing the task:

@@

\subsubsection{Fighting Mac's Security Features}
The biggest usability obstacle was the result of tensions between Mac's Gatekeeper 
code-signing feature on OS X, which prevents users from opening unsigned code 
downloaded from the Internet to execute on their machine unless overridden through
managing system preferences. Surprisingly, the feature which impacted Tor's usability
the most was the tension between a security precaution, and Tor's decision to self-sign
their downloads, rather than a specific feature of the Tor Browser itself. We found that 
encountering the Gatekeeper will cause frustration to most users, and may be enough 
to stop our participants in the download process:

@@

As a result, Tor has developed a step-by-step visual guide on the download page to 
help Mac OS X users to bypassing the Gatekeeper during their download.

\subsubsection{On Visual Communication}
Our participants did not read much of the text provided on the download page or elsewhere during 
the experiment. Critical actions were predominantly guided by visual cues:

@@

Prudently and selectively incorporating visual elements into user interface design may be the key to 
communicating with users and guiding correct user behaviors.

\subsubsection{User Comprehension}

Most of our participants did not have the expertise to understand 
the advanced settings for the Tor Browser:

@@

There was one participant who communicated a correct and thorough understanding of the 
new identity feature:

@@

Notice that this user explained what the feature can do for him, rather than how the 
feature works. For the end user, the reason why a security feature is employed is what 
makes a feature valuable and thus motivates them to use the feature. Communicating why a 
feature is present may be more effective for increasing use of advanced features 
than communicating the technical details of how a feature works.

@@

\indent \indent Because of the limited size of the study, it's not possible to state with confidence what 
fraction of users will encounter major usability obstacles. However, it was effective at discovering 
and demonstrating issues that are likely to cause problems for many users. 
People did have difficulty with installing Tor Browser (principally because of the Gatekeeper 
code-signing feature on OS X), did not understand what many of the toolbar options meant, 
and were confused by most Tor-specific behaviors. For specific problems 
encountered by an individual user, we refer you to our resources online.

@@

\indent \indent If you would like to observe individual participants' cognitive walkthroughs, 
we transcribed the audio files from our experiment
and synced them to the screen capture we took during the duration of the experiment.
Figure~\ref{walkthrough} shows a screenshot of one of the videos.
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
\end{itemize}
